---
title: "Lab 10 - just some useful things"
author: "Sarah Lam"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(usethis)
library(janitor)

#New packages
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```


## beepr beeps

Use the function `beep()` in the beeper package to make an audio alert when your code is done running. 
```{r, eval = FALSE}
for (i in rev(seq(1:999))) {
  
  print(paste(i, "bottles of beer on the wall")) #for loop - iterates function for each value in a sequence 
  
}

#beep(4)
```

#Praise and cowsay 

packages built with a single purpose: to be kind and fun. 

```{r}
praise("${Exclamation}, ${EXCLAMATION}...${exclamation}!!!!")

praise("Holy ${creating}, Batman - this code is ${ADJECTIVE}!")
```

Use cowsay::say() to make a character say something to you. 

```{r}
cowsay::say(praise::praise("You're doing ${ADJECTIVE} today!!"), by = "trilobite")
```

How to make a non-version controlled rproj, a version controlled repo with git
- In console run `usethis::use_git()`
- Then run `usethis::use_github()` also in console

## Use paletteer to access thousands of color palettes

```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm =TRUE)) %>% 
  slice_min(n = 10, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("palettetown::miltank")
```


## One spatial data example 

```{r}
vegetation <- read_sf("doc.kml") %>% 
  select(Name) %>% 
  clean_names()

ggplot(data = vegetation) +
  geom_sf(aes(fill = name), color = NA) +
  theme_minimal() +
  scale_fill_paletteer_d("ggthemes::manyeys") +
  labs(title = "Jornada Basin LTER Vegetation",
       caption = "Source: Jornada LTER")
 
```

```{r}
ggsave(filename = "my_awesome_map.jpg", width = 8, height = 5)
```


